\documentclass[addpoints]{exam}
% leqno 將方程式編號放在左側

%\printanswers

\usepackage[top=2.5cm,bottom=2cm,left=2.5cm,right=2.5cm,headsep=10pt,a4paper]{geometry} % 引用頁面幾何套件，設定頁面邊界

\usepackage{siunitx} % 角度
% \input{NewCommands}

\usepackage{amsmath,amssymb,amsthm} % 引用常見的數學符號與設定


\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{theorem}{Theorem}
\newtheorem{remark}{Remark}
\newtheorem{prop}{Proposition}
\newtheorem{lemma}{Lemma}

\usepackage{lastpage} % 取得最後頁碼




\usepackage{graphicx} % 引用圖檔內嵌入套件
\graphicspath{{Pictures/}} % 設定圖檔目錄
\usepackage{xcolor} %引用顏色套件
\usepackage{enumerate}
\usepackage{float}
\usepackage{hyperref}
\usepackage{mdwlist} % use suspend & resume to successive enumerate

\usepackage{CJKutf8} % 設定中文

\def \lflr{\left\lfloor} %自定義 floor function
\def \rflr{\right\rfloor} %自定義

% question separation
\renewcommand{\questionshook}{%
  \setlength{\itemsep}{0.5cm}%
}

\allowdisplaybreaks %equation allowed to next page

\firstpageheader{\today}
                {}
                {}
\footer{}{\sf Page \thepage~of~\pageref{LastPage}}{}

\begin{document}

\begin{CJK*}{UTF8}{gbsn}
% Title
\begin{center}
    {\Large{\bf Introduction to Mathematical Analysis\\
    Homework 7  Due  November  7  (Friday), 2025\\
    Please submit your homework online in PDF format.
  %  Homework X Brief Solution
  }} \\ 
    \large
    %\text{Due date: 3/9/2023}
\end{center}

\noindent\rule{16.2cm}{0.4pt}


\begin{questions}


% ============ Question x ============
\question  (15 pts)  

 Assume that $(S,d)$ is a metric space, and let $f_n, f : S \to \mathbb{R}$ be real-valued functions.  
Suppose that $f_n \to f$ uniformly on $S$, and there exists a constant $M > 0$ such that
\[
|f_n(x)| \le M \quad \text{for all } x \in S \text{ and all } n.
\]
Let $g : \overline{B(0;M)} \to \mathbb{R}$ be continuous, where
\[
B(0;M) = \{ y \in \mathbb{R} : |y| < M \}.
\]
Define
\[
h_n(x) = g(f_n(x)), \qquad h(x) = g(f(x)), \quad x \in S.
\]
Prove that $h_n \to h$ uniformly on $S$.



\begin{solution}
 \end{solution}
 
 
 
 \question (15 pts) 
Let $f_n(x) = x^n$. The sequence $\{f_n\}$ converges pointwise but not uniformly on $[0,1]$.
Let $g$ be continuous on $[0,1]$ with $g(1) = 0$. 
Prove that the sequence $\{ g(x) x^n \}$ converges uniformly on $[0,1]$.



\begin{solution}
 \end{solution}
 
 
 \question (15 pts)
Assume that $g_{n+1}(x) \le g_n(x)$ for each $x$ in $T$ and each $n = 1, 2, \ldots$, 
and suppose that $g_n \to 0$ uniformly on $T$. 
Prove that 
\[
\sum (-1)^{n+1} g_n(x)
\]
converges uniformly on $T$.


\begin{solution}
 \end{solution}
 
 \question (15  pts)
  \[
f_n(x) = \frac{x}{1 + n x^2}, \quad x \in \mathbb{R}, \; n = 1, 2, \ldots
\]
Find the limit function $f$ of the sequence $\{ f_n \}$ and the limit function $g$ of the sequence $\{ f_n' \}$.

\begin{enumerate}[(a)]
\item Prove that $f'(x)$ exists for every $x$ but that $f'(0) \ne g(0)$. 
For what values of $x$ is $f'(x) = g(x)$?

\item In what subintervals of $\mathbb{R}$ does $f_n \to f$ uniformly?

\item In what subintervals of $\mathbb{R}$ does $f_n' \to g$ uniformly?
\end{enumerate}

\begin{solution}
 \end{solution}


 \question (15 pts) 
Prove that 
\[
\sum x^n (1 - x)
\]
converges pointwise but not uniformly on $[0,1]$, whereas 
\[
\sum (-1)^n x^n (1 - x)
\]
converges uniformly on $[0,1]$. 
This illustrates that uniform convergence of $\sum f_n(x)$ along with pointwise convergence of $\sum |f_n(x)|$ does not necessarily imply uniform convergence of $\sum |f_n(x)|$.



\begin{solution}
 \end{solution}
 
 \question (15 pts) 
Let 
\[
f_n(x) = \frac{1}{n} e^{-n^2 x^2}, \quad x \in \mathbb{R}, \; n = 1, 2, \ldots
\]
Prove that $f_n \to 0$ uniformly on $\mathbb{R}$, that $f_n' \to 0$ pointwise on $\mathbb{R}$,
but that the convergence of $\{ f_n' \}$ is not uniform on any interval containing the origin.



\begin{solution}
 \end{solution}
 
 
 \question (10 pts) 
Let $\{ f_n \}$ be a sequence of real-valued continuous functions defined on $[0,1]$
and assume that $f_n \to f$ uniformly on $[0,1]$. 
Prove or disprove
\[
\lim_{n \to \infty} \int_{0}^{1 - 1/n} f_n(x) \, dx = \int_{0}^{1} f(x) \, dx.
\]


\begin{solution}
 \end{solution}
\end{questions}


You can do the following problems to practice. You don't have to submit the following problems.

\begin{questions}

\question   Prove that the series 
\[
\zeta(s) = \sum_{n=1}^{\infty} n^{-s}
\]
converges uniformly on every half-infinite interval 
\[
1 + h \le s < +\infty,
\]
where $h > 0$. Show that the equation
\[
\zeta'(s) = - \sum_{n=1}^{\infty} \frac{\log n}{n^s}
\]
is valid for each $s > 1$, and obtain a similar formula for the $k$th derivative $\zeta^{(k)}(s)$.

\begin{solution}

\end{solution}
\medskip

\question If $r$ is the radius of convergence of 
\[
\sum a_n (x - x_0)^n,
\]
where each $a_n \ne 0$, show that
\[
\liminf_{n \to \infty} \left| \frac{a_n}{a_{n+1}} \right|
   \le r \le 
   \limsup_{n \to \infty} \left| \frac{a_n}{a_{n+1}} \right|.
\]
\begin{solution}

\end{solution}

\medskip

\question Prove that the series
\[
\sum_{n=0}^{\infty} \left( \frac{x^{2n+1}}{2n+1} - \frac{x^{n+1}}{2n+2} \right)
\]
converges pointwise but not uniformly on $[0,1]$.
\begin{solution}

\end{solution}

\medskip

\question   Prove that 
\[
\sum_{n=1}^{\infty} a_n \sin nx 
\quad \text{and} \quad
\sum_{n=1}^{\infty} a_n \cos nx
\]
are uniformly convergent on $\mathbb{R}$ if 
\[
\sum_{n=1}^{\infty} |a_n|
\]
converges.
\begin{solution}
\end{solution}

\question Let $\{a_n\}$ be a decreasing sequence of positive terms. 
Prove that the series 
\[
\sum a_n \sin nx
\]
converges uniformly on $\mathbb{R}$ if and only if $n a_n \to 0$ as $n \to \infty$.

\begin{solution}

\end{solution}



\end{questions}


%
% \appendix
% \section{}
\end{CJK*}
\end{document}

\question

\begin{solution}

\end{solution}
