\lecture{17}{30 April.}{}
As discussed in the previous section, limits and integrals cannot in general be interchanged. That is, even if \(f_n \to f\) pointwise on \(\Omega\), it may happen that 
\[
    \lim_{n \to \infty} \int _\Omega f_n \neq \int _\Omega \lim_{n \to \infty} f_n.  
\]  
Thus, in order to justify passing a limit through an integral, one needs an additional hypothesis. The Lebesgue dominated convergence theorem provides one of the most useful such criteria: if the sequence is dominated by a single absolutely integrable function, then the interchange of limit and integral is valid. 

\begin{theorem}[Lebesgue dominated convergence theorem]
    Let \(\Omega \) be a measurable subset of \(\mathbb{R} ^n\), and let \(f_1, f_2, \dots\) be measurable functions from \(\Omega\) to \(\mathbb{R} ^*\) such that \(f_n(x)\) converges pointwise for every \(x \in \Omega\). Suppose moreover that there exists an absolutely integrable function \(F: \Omega \to [0, \infty]\) such that \(\vert f_n(x) \vert \le F(x) \) for all \(x \in \Omega\) and all \(n \ge 1\). Then, if we write \(f(x) \coloneqq \lim_{n \to \infty} f_n (x)  \), we have
    \[
        \int _\Omega f = \lim_{n \to \infty} \int _\Omega f_n.
    \]            
\end{theorem}

\begin{proof}
    Since \(F\) is non-negative, measurable, and absolutely integrable, we knoe \(F < \infty\) almost everywhere by \autoref{lm: finite integral implies infty set has measure 0}. In other words, \(E \coloneqq \left\{ x \in \Omega: F(x) = + \infty \right\} \) has measure zero. If we replace \(\Omega\) by \(\Omega \setminus E\), then none of the relevant integrals changes, because deleting a measure zero set does not affect the integral of an absolutely integrable function. Hence, without loss of generality, we may assume from now on that \(F(x) < \infty\) for every \(x \in \Omega\). Since \(\vert f_n(x) \vert \le F(x) \) for all \(n\), this also implies that each \(f_n(x)\) is finite for every \(x \in \Omega\). 

    Because each \(f_n\) is measurable and \(f_n \to f\) pointwise, \(f\) is measurable by \autoref{lm: sup, inf, limsup, liminf of measurable func are measurable}. Next, since \(\vert f_n(x) \vert \le F(x) \) for all \(n\) and all \(x \in \Omega\), we may pass to the limit in \(n\) and obtain 
    \[
        \vert f(x) \vert \le F(x) \quad \text{for all } x \in \Omega.   
    \]                  
    Therefore,
    \[
        \int _\Omega \vert f \vert \le \int _\Omega F < \infty, 
    \]
    so \(f\) is absolutely integrable. The same argument can shows that \(f_n\) is absolutely integrable, because 
    \[
        \int _\Omega \vert f_n \vert \le \int _\Omega F < \infty. 
    \] 
    Thus, all of the integrals appearing below are finite and well-defined.

    For each \(n\) and each \(x \in \Omega\), we have \(\vert f_n(x) \vert \le F(x) \). Hence, 
    \[
        -F(x) \le f_n(x) \le F(x).
    \]   
    It follows that \(F(x) + f_n(x) \ge 0\) for all \(x \in \Omega\). So the function \(F + f_n\) are non-negative and measurable. Moreover, since \(f_n(x) \to f(x)\), we also have 
    \[
        F(x) + f_n(x) \to F(x) + f(x) \quad \text{pointwise on } \Omega. 
    \]    
    \hyperref[lm: Fatou]{Fatou's lemma} therefore gives
    \[
        \int _\Omega (F + f) = \int _\Omega \liminf_{n \to \infty} (F + f_n) \le \liminf_{n \to \infty} \int _\Omega (F + f_n). 
    \] 
    Using additivity of the integral for absolutely integrable functions, this becomes
    \[
        \int _\Omega F + \int _\Omega f \le \liminf_{n \to \infty} \left( \int _\Omega F + \int _\Omega f_n \right).  
    \]
    Since \(\int _\Omega F\) is a fixed finite number, we may subtract it from both sides and obtain 
    \[
        \int _\Omega f \le \liminf_{n \to \infty} \int _\Omega f_n. 
    \] 

    Similarly, since \(\vert f_n(x) \vert \le F(x) \), we have \(F(x) - f_n(x) \ge 0\) for all \(x \in \Omega\). Thus, \(F - f_n\) is non-negative and measurable for all \(n\). Since \(f_n(x) \to f(x)\) pointwise, we also have 
    \[
        F(x) - f_n(x) \to F(x) - f(x) \quad \text{pointwise on } \Omega. 
    \]     
    Applying \hyperref[lm: Fatou]{Fatou's lemma} once more, we obtain 
    \[
        \int _\Omega (F - f) = \int _\Omega \liminf_{n \to \infty} \left( F - f_n  \right) \le \liminf_{n \to \infty} \int _\Omega (F - f_n).  
    \] 
    By additivity,
    \[
        \int _\Omega F - \int _\Omega f \le \liminf_{n \to \infty} \left( \int _\Omega F - \int _\Omega f_n \right) = \int _\Omega F - \textcolor{red}{\limsup_{n \to \infty}} \int _\Omega f_n.   
    \]
    This gives 
    \[
        \int _\Omega f \ge \limsup_{n \to \infty} \int _\Omega f_n. 
    \]
    
    Now we have 
    \[
        \limsup_{n \to \infty} \int _\Omega f_n \le \int _\Omega f \le \liminf_{n \to \infty} \int _\Omega f_n.  
    \]
    But for real sequence \((a_n)\)  we always has 
    \[
      \liminf_{n \to \infty} a_n \le \limsup_{n \to \infty} a_n.    
    \]
    Therefore, the only possibility is that
    \[
        \liminf_{n \to \infty} \int _\Omega f_n = \limsup_{n \to \infty} \int _\Omega f_n = \int _\Omega f.  
    \]
    Hence, the sequence \((\int _\Omega f_n)\) converges, and its limit is \(\int _\Omega f\) by \autoref{thm: linf eq lsup eq f, then converge}. That is, 
    \[
        \lim_{n \to \infty} \int _\Omega f_n = \int _\Omega f. 
    \] 
    This proves the dominated convergence theorem.
\end{proof}

Finally, we record a lemma which is not particularly interesting in itself, but we will have some useful consequences later in these notes. 

\begin{definition}[Upper and lower Lebesgue integral]
    Let \(\Omega\) be a measurable subset of \(\mathbb{R} ^n\), and let \(f: \Omega \to \mathbb{R}\) (not necessarily measurable). We define the upper Lebesgue integral \(\overline{\int _\Omega} f\) to be 
    \[
        \overline{\int _\Omega } f \coloneqq \inf \left\{ \int _\Omega g: g \text{ is an absolutely integrable function from } \Omega \text{ to } \mathbb{R} \text{ that majorizes } f    \right\}, 
    \]    
    and the lower Lebesgue integral \(\underline{\int _\Omega} f\) to be 
    \[
        \underline{\int _\Omega} f \coloneqq \sup \left\{ \int _\Omega g: g \text{ is an absolutely integrable function from } \Omega \text{ to } \mathbb{R} \text{ that minorizes } f  \right\}.
    \] 
\end{definition}

We first record two elementary consequences of this definition. 

It is easy to see that 
\[
    \underline{\int _\Omega } f \le \overline{\int _\Omega } f.  
\]
Next, suppose \(f\) is absolutely integrable. Then \(f\) is both an absolutely integrable minorant and an absolutely integrable majorant of itself. Therefore,
\[
    \underline{\int _\Omega } f = \sup \left\{ \int _\Omega u: u \text{ is absolutely intergable and } u \le f  \right\} \ge \int _\Omega f.  
\]  
On the other hand, if \(u \le f\) for some absolutely integrable \(u\), then 
\[
    \int _\Omega u \le \int _\Omega f.
\]  
Taking the supremum over all absolutely integrable \(u \le f\), we obtain 
\[
    \underline{\int _\Omega } f \le \int _\Omega f. 
\] 
Hence, \(\underline{\int _\Omega } f = \int _\Omega f \).

Similarly, since \(f\) is an absolutely integrable majorant of itself, 
\[
    \overline{\int _\Omega } f = \inf \left\{ \int _\Omega v: v \text{ is absolutely integrable and } f \le v   \right\} \le \int _\Omega f.  
\]
Conversely, if \(f \le v\) for some absolutely integrbale \(v\), then 
\[
    \int _\Omega f \le \int _\Omega v.
\]  
Taking the infimum over all absolutely integrbale \(v \ge f\), we get \(\int _\Omega f \le \overline{\int _\Omega} f\). Thus, \(\overline{\int _\Omega } f = \int _\Omega f.\) 
Consequently, whenever \(f\) is absolutely integrable,
\[
    \underline{\int _\Omega } f = \int _\Omega f = \overline{\int _\Omega } f.  
\] 
The converse is also true:
\begin{lemma} \label{lm: upper integral and lower integral are same implies absolutely integrable}
    Let \(\Omega \) be a measurable subset of \(\mathbb{R} ^n\), and let \(f: \Omega \to \mathbb{R} \) be a function, not assumed a priori to be measurable. Suppose that there exists \(A \in \mathbb{R}\) s.t. 
    \[
        \overline{\int _\Omega } f = \underline{\int _\Omega} f = A. 
    \]    
    Then \(f\) is absolutely integrable, and 
    \[
       \int _\Omega f = \overline{\int _\Omega } f = \underline{\int _\Omega} f = A. 
    \] 
\end{lemma}

\begin{proof}
    We will show that \(f\) agree almost everywhere with an absolutely integrable function, and hence \(f\) itself is absolutely integrable with integral \(A\). 

    By definition,
    \[
        \overline{\int _\Omega f} = \inf \left\{ \int _\Omega g: g \text{ is absolutely integrable and } g \ge f  \right\}.  
    \]   
    Since this infimum is equal to \(A\), for every \(n \ge 1\), there exists an absolutely integrable function \(f_n^+: \Omega \to \mathbb{R}\) s.t. \(f_n^+\) majorizes \(f\) and
    \[
        \int _\Omega f_n^+ \le A + \frac{1}{n}.
    \]     
    Similarly, since 
    \[
        A = \underline{\int _\Omega } f = \sup \left\{ \int _\Omega g: g \text{ is absolutely integrable and } g \le f \right\},  
    \]
    for every integer \(n \ge 1\) there exists an absolutely integrable function \(f_n^-: \Omega \to \mathbb{R}\) s.t. \(f_n^-\) minorizes \(f\) and 
    \[
        \int _\Omega f_n^- \ge A - \frac{1}{n}.
    \]   
    Thus, for every \(n\) we have \(f_n^- \le f \le f_n^+\) on \(\Omega\).

    Now set 
    \[
        F^+(x) \coloneqq \inf _{n \ge 1} f_n^+ (x), \quad F^-(x) \coloneqq \sup _{n \ge 1} f_n^-(x), \quad x \in \Omega.
    \]   
    Since each \(f_n^+\) and \(f_n^-\) is measurable, we know \(F^+\) and \(F^-\) are measurable by \autoref{lm: sup, inf, limsup, liminf of measurable func are measurable}. Since \(f(x) \le f_n^+(x)\) for all \(n\), we have 
    \[
        f(x) \le \inf _{n \ge 1} f_n^+(x) = F^+(x).
    \]       
    Similarly, we have 
    \[
        F^-(x) = \sup _{n \ge 1} f_n^-(x) \le f(x).
    \]
    Hence, 
    \[
        F^-(x) \le f(x) \le F^+(x) \quad \forall x \in \Omega.
    \]

    We first consider \(F^+\). Since \(F^+ \le f_1^+\) pointwise and \(f_1^+\) is absolutely integrable, we would like to conclude that \(F^+\) is also absolutely integrable. For this we also need a lower bound by an absolutely integrable functoin. 

    Because \(f_n^- \le f \le F^+\) for every \(n\), in particular we have 
    \[
        f_1^- \le F^+ \le f_1^+.
    \]      
    Hence,
    \[
        \vert F^+ \vert \le \max \left\{ \left\vert f_1^- \right\vert, \left\vert f_1^+ \right\vert   \right\} \le \vert f_1^- \vert + \vert f_1^+ \vert.   
    \]
    Since \(f_1^-\) and \(f_1^+\) are absolutely integrable, so is \(\vert f_1^- \vert + \vert f_1^+ \vert  \). By comparison, \(F^+\) is absolutely integrable. 

    The same argument applies to \(F^-\), by \(f_1^- \le F^- \le f_1^+\), we have 
    \[
        \vert F^- \vert \le \vert f_1^- \vert + \vert f_1^+ \vert  
    \]   
    and thus \(F^-\) is also absolutely integrable.

    Now since \(F^+ \le f_n^+\) for all \(n\) and they are both absolutely integrable, 
    \[
        \int _\Omega F^+ \le \int _\Omega f_n^+ \le A + \frac{1}{n} \quad \forall n \ge 1.
    \]    
    Letting \(n \to \infty\), we obtain 
    \[
        \int _\Omega F^+ \le A.
    \] 
    Similarly, we have 
    \[
        A - \frac{1}{n} \le \int _\Omega f_n^- \le \int _\Omega F^-.
    \]
    Letting \(n \to \infty\), we have 
    \[
        A \le \int _\Omega F^-.
    \] 
    On the other hand, since \(F^- \le F^+\) pointwise, we have 
    \[
        \int _\Omega F^- \le \int _\Omega F^+.
    \] 
    Combining the three inequalities,
    \[
        A \le \int _\Omega F^- \le \int _\Omega F^+ \le A.
    \]
    Thus,
    \[
        \int _\Omega F^- = \int _\Omega F^+ = A.
    \]

    Now since 
    \[
        \int _\Omega (F^+ - F^-) = \int _\Omega F^+ - \int _\Omega F^- = A - A = 0,
    \]
    we know \(F^+ - F^-\) is zero almost everywhere since \(F^+ - F^-\) is a non-negative measurable function. Hence, \(F^+ = F^-\) almost everywhere on \(\Omega\).    

    Recall that 
    \[
        F^-(x) \le f(x) \le F^+(x) \quad \forall x \in \Omega.
    \]
    At every point where \(F^+(x) = F^-(x)\), we have 
    \[
        f(x) = F^+(x) = F^-(x).
    \]
    Since \(F^+ = F^-\) almost everywhere, it follows that \(f = F^+\) almost everywhere. Now \(F^+\) is measurable and absolutely integrable. A function which agrees almost everywhere with a measurable function is measurable by \autoref{thm: almost equal to measurable func then measurable}, so \(f\) is measurable. Also, \(\vert f \vert = \vert F^+ \vert  \) almost everywhere, and therefore 
    \[
        \int _\Omega \vert f \vert = \int _\Omega \vert F^+ \vert < \infty.  
    \]     
    Thus, \(f\) is absolutely integrable. 
    
    Finally, since \(f = F^+\) almost everywhere, we have 
    \[
        \int _\Omega f = \int _\Omega F^+ = A.
    \]
    Therefore,
    \[
        \int _\Omega f = \overline{\int _\Omega } f = \underline{\int _\Omega } f = A.  
    \]
\end{proof}

\section{Comparison with the Riemann Integral}
We have spent a lot of effort constructing the Lebesgue integral, but have not yet addressed the question of how to actually compute any Lebesgue integrals, and whether Lebesgue integration is any dierent from the Riemann integral (say for integrals in one dimension). We now show that the Lebesgue integral is a generalization of the Riemann integral. To clarify the following discussion, we shall temporarily distinguish the Riemann integral from the Lebesgue integral by writing the Riemann integral as \(R. \int _I f\). Recall that, in the definition of the Riemann integral on a bounded interval \(I \subseteq \mathbb{R}\), one starts with a bounded function \(f: I \to \mathbb{R}\). The boundedness of both the interval I and the function f will be important. Our objective
in this section is to prove that every Riemann integrable function on a bounded interval is Lebesgue integrable, indeed absolutely integrable, and that the two integrals agree.

\begin{proposition}
    Let \(I \subseteq \mathbb{R}\) be a bounded interval, and let \(f: I \to \mathbb{R}\) be a Riemann integrable function. Then \(f\) is also absolutely integrable, and 
    \[
        \int _I f = R. \int _I f.
    \]  
\end{proposition}

\begin{proof}
    Write \(A \coloneqq R. \int _I f\). Since \(f\) is Riemann integrable, \(f\)'s upper integral and lower integral agrees, and thus for every \(\varepsilon > 0\), there exists a partition \(\mathcal{P}\) of \(I\) into finitely many subintervals \(J\) s.t. 
    \[
        A - \varepsilon \le \sum_{J \in \mathcal{P}} \vert J \vert \inf _{x \in J} f(x) \le A \le \sum_{J \in \mathcal{P}} \vert J \vert \sup _{x \in J} f(x) \le A + \varepsilon,
    \]      
    where \(\vert J \vert \) represents the length of \(J\). Note that \(m(J) = \vert J \vert \) since \(J\) is a one-dimensional box. 
    
    Define simple functions
    \[
        f_{\varepsilon}^-(x) = \sum_{J \in \mathcal{P}} \left( \inf _{t \in J} f(t) \right) \chi _J(x), \quad f_{\varepsilon}^+(x) = \sum_{J \in \mathcal{P}} \left( \sup _{t \in J} f(t) \right) \chi _J(x). 
    \]
    By construction, we have \(f_{\varepsilon}^- \le f \le f_{\varepsilon}^+\) pointwise on \(I\). Note that \(f_{\varepsilon }^-, f_{\varepsilon}^+ \) are simple, and thus measurable. Moreover, since \(I\) is bounded, so it has finite measure, so \(f_{\varepsilon}^-\) and \(f_{\varepsilon}^+\) are absolutely integrable. Also, 
    \[
        \int _I f_{\varepsilon }^- = \sum_{J \in \mathcal{P}} \inf _{t \in J} f(t) \cdot \vert J \vert, \quad \int _I f_{\varepsilon}^+ = \sum_{J \in \mathcal{P}} \sup _{t \in J} f(t) \cdot \vert J \vert.
    \]
    Therefore,
    \[
        A - \varepsilon \le \int _I f_{\varepsilon}^- \         \le A \le \int _I f_{\varepsilon}^+ \le A + \varepsilon.
    \] 
    Since \(f_{\varepsilon }^+ \) majorizes \(f\), and \(f_{\varepsilon}^+ \) is absolutley integrable, by definition we have \(\overline{\int _I} f \le \int _I f_{\varepsilon}^+ \). Similarly, since \(f_{\varepsilon}^- \) minorizes \(f\) and is absolutely integrable, we have \(\underline{\int _I} f \ge \int _I f_{\varepsilon}^- \). Hence,
    \[
        A - \varepsilon \le \underline{\int _I} f \le \overline{\int _I} f \le A + \varepsilon \quad \forall \varepsilon > 0.
    \]     
    This shows that \(\underline{\int _I} f = \overline{\int _I} f = A\). By the previous lemma, \(f\) is absolutely integrable and \(\int _I f = A\). Thus, 
    \[
        \int _I f = R. \int _I f.
    \]
\end{proof}