\documentclass[addpoints]{exam}
% leqno 將方程式編號放在左側

\printanswers

\usepackage[top=2.5cm,bottom=2cm,left=2.5cm,right=2.5cm,headsep=10pt,a4paper]{geometry} % 引用頁面幾何套件，設定頁面邊界

\usepackage{siunitx} % 角度
% \input{NewCommands}

\usepackage{amsmath,amssymb,amsthm} % 引用常見的數學符號與設定


\theoremstyle{definition}
\newtheorem*{definition*}{Definition}
\newtheorem*{theorem}{Theorem}
\newtheorem*{remark}{Remark}
\newtheorem*{claim}{Claim}
\newtheorem*{proposition}{Proposition
}
\usepackage{lastpage} % 取得最後頁碼




\usepackage{graphicx} % 引用圖檔內嵌入套件
\graphicspath{{Pictures/}} % 設定圖檔目錄
\usepackage{xcolor} %引用顏色套件
\usepackage{enumerate}
\usepackage{float}
\usepackage{hyperref}
\usepackage{mdwlist} % use suspend & resume to successive enumerate

\usepackage{CJKutf8} % 設定中文

\def \lflr{\left\lfloor} %自定義 floor function
\def \rflr{\right\rfloor} %自定義

% question separation
\renewcommand{\questionshook}{%
  \setlength{\itemsep}{0.5cm}%
}

\allowdisplaybreaks %equation allowed to next page

\firstpageheader{}
                {}
                {}
\footer{}{\sf Page \thepage~of~\pageref{LastPage}}{}

\begin{document}

\begin{CJK*}{UTF8}{gbsn}
% Title
\begin{center}
   {\Large{\bf Introduction to Mathematical Analysis\\
    Homework 12 Due  December  12  (Friday), 2025\\
    Please submit your homework online in PDF format.
  %  Homework X Brief Solution
  }} \\ 
    \large
    %\text{Due date: 3/9/2023}
\end{center}

\noindent\rule{16.2cm}{0.4pt}


\begin{questions}


% ============ Question x ============
\question (20 pts) \textbf{Exercise 5.4.1}  
Show that if $f:\mathbb{R}\to\mathbb{C}$ is both compactly supported and 
$\mathbb{Z}$--periodic, then it is identically zero.

Hint: A function $f:\mathbb{R}\to\mathbb{C}$ is said to be \emph{compactly supported}
if the set
\[
\operatorname{supp}(f)
:= \overline{\{\,x\in\mathbb{R} : f(x)\neq 0\,\}}
\]
is a compact subset of $\mathbb{R}$.
Equivalently, $f$ is compactly supported if there exists a bounded closed interval
$[a,b]\subset\mathbb{R}$ such that
\[
f(x)=0 \qquad \text{whenever } x\notin[a,b].
\]


\question (20 pts) (Exercise 5.5.1)
Let $f$ be a function in $C(\mathbf{R}/\mathbf{Z};\mathbf{C})$, and define the
\emph{trigonometric Fourier coefficients} $a_n,b_n$ for $n=0,1,2,\dots$ by
\[
a_n := 2\int_{0}^{1} f(x)\cos(2\pi n x)\,dx,\qquad
b_n := 2\int_{0}^{1} f(x)\sin(2\pi n x)\,dx.
\]

\begin{enumerate}[(a)]
\item Show that the series
\[
\frac12 a_0+\sum_{n=1}^\infty \bigl(a_n \cos(2\pi n x)+b_n\sin(2\pi n x)\bigr)
\]
converges to $f$ in the $L^2$–metric.

\item Show that if $\sum_{n=1}^\infty |a_n|$ and $\sum_{n=1}^\infty |b_n|$ are absolutely
convergent, then the above series actually converges \emph{uniformly} to $f$ (and not just in $L^2$).
\end{enumerate}


\question (20 pts) (Exercise 5.5.2)
Let $f(x)$ be the function defined by $f(x)=(1-2x)^2$ when $x\in [0,1]$,
and extended to be $\mathbf{Z}$–periodic on $\mathbf{R}$.

\begin{enumerate}[(a)]
\item Using Exercise 5.5.1, show that the series
\[
\frac13+\sum_{n=1}^\infty \frac{4}{\pi^2 n^2}\cos(2\pi n x)
\]
converges uniformly to $f$. (You may use the fact that 
\[
\int_0^1 x\,e^{-2\pi i n x}\,dx
=
-\frac{1}{2\pi i n},
\qquad (n\neq 0),
\]
\[
\int_0^1 x^2\,e^{-2\pi i n x}\,dx
=
-\frac{1}{2\pi i n}
+\frac{2}{(2\pi n)^2},
\qquad (n\neq 0).
\])

\item Conclude that
\[
\sum_{n=1}^\infty \frac{1}{n^2}=\frac{\pi^2}{6}.
\]

\item Conclude that
\[
\sum_{n=1}^\infty \frac{1}{n^4}=\frac{\pi^4}{90}.
\]
(Hint: expand the cosines in terms of exponentials and use Plancherel’s theorem.)
\end{enumerate}


\question (20 pts)  (Exercise 5.5.3)
If $f\in C(\mathbf{R}/\mathbf{Z};\mathbf{C})$ and $P$ is a trigonometric
polynomial, show that
\[
\widehat{f*P}(n) = \widehat f(n)\,c_n = \widehat f(n)\,\widehat P(n)
\]
for all integers $n$, where $c_n$ are the Fourier coefficients of $P$.
More generally, if $f,g\in C(\mathbf{R}/\mathbf{Z};\mathbf{C})$, show that
\[
\widehat{f*g}(n)=\widehat f(n)\,\widehat g(n)
\quad\text{for all }n\in\mathbf{Z}.
\]


\question  (20 pts) (Exercise 5.5.4)
Let $f\in C(\mathbf{R}/\mathbf{Z};\mathbf{C})$ be differentiable, and assume its derivative
$f'$ is also continuous. Show that
\[
\sum_{n=-\infty}^\infty |n\,\widehat f(n)|^2<\infty
\]
and that the Fourier coefficients of $f'$ satisfy
\[
\widehat{f'}(n)=2\pi i n\,\widehat f(n)\qquad\text{for all }n\in\mathbf{Z}.
\]

\end{questions}


You can do the following problem for practice. You don't have to turn in the following problems.
\begin{questions}

%------------------------------------------------------------------%
\question (5.5.5)
Let $f,g\in C(\mathbb{R}/\mathbb{Z};\mathbb{C})$.  Prove the Parseval
identity
\[
\Re\int_0^1 f(x)\overline{g(x)}\,dx
  = \Re\sum_{n\in\mathbb{Z}} \widehat f(n)\,\overline{\widehat g(n)}.
\]
(Hint: apply the Plancherel theorem to $f+g$ and $f-g$, and subtract the
two.)  Then conclude that the real parts can be removed, i.e.
\[
\int_0^1 f(x)\overline{g(x)}\,dx
  = \sum_{n\in\mathbb{Z}} \widehat f(n)\,\overline{\widehat g(n)}.
\]
(Hint: apply the first identity with $f$ replaced by $if$.)

%------------------------------------------------------------------%
\question (5.5.6)
In this exercise we develop Fourier series for functions of an arbitrary
period $L>0$.

Let $L>0$ and let $f:\mathbb{R}\to\mathbb{C}$ be a continuous $L$-periodic
function.  For each integer $n$ define
\[
c_n := \frac1L\int_{0}^{L} f(x)\,e^{-2\pi i n x/L}\,dx.
\]

\begin{itemize}
\item[(a)]
Show that the series
\[
\sum_{n=-\infty}^{\infty} c_n\,e^{2\pi i n x/L}
\]
converges to $f$ in $L^2$-metric.  More precisely, prove that
\[
\lim_{N\to\infty}\int_{0}^{L}
\Bigl| f(x)-\sum_{n=-N}^{N} c_n\,e^{2\pi i n x/L}\Bigr|^2 dx = 0.
\]
(Hint: apply the Fourier theorem to the function $f(Lx)$.)

\item[(b)]
If the series $\sum_{n=-\infty}^{\infty} |c_n|$ is absolutely convergent,
show that
\[
\sum_{n=-\infty}^{\infty} c_n\,e^{2\pi i n x/L}
\]
converges \emph{uniformly} to $f$.

\item[(c)]
Show that
\[
\frac1L\int_{0}^{L} |f(x)|^2\,dx
   = \sum_{n=-\infty}^{\infty} |c_n|^2.
\]
(Hint: apply the Plancherel theorem to the function $f(Lx)$.)
\end{itemize}

\end{questions}


% \appendix
% \section{}
\end{CJK*}
\end{document}