\begin{problem}
Let \(V\) be the set of real numbers. Regard \(V\) as a vector space over the field of rational numbers, with the usual operations. Prove that this vector space is not finite-dimensional.
\end{problem}
\begin{proof}
    Consider the set \(S = \left\{ \log 2, \log 3, \dots  \right\} \), which is the set 
    \[
        \left\{ \log p \mid p \text{ is prime} \right\}. 
    \] Now suppose there are rational numbers \(\alpha _i\) s.t. 
    \[
        \alpha _1 \log 2 + \alpha _2 \log 3 +\alpha _3 \log 5 + \dots = 0.
    \] Then we know 
    \[
        \log \left( 2^{\alpha _1} 3^{\alpha _2} 5^{\alpha _3} \dots \right) = 0.
    \]
    However, the logarithm is strictly increasing, so we know \(\alpha _i = 0\) for all \(i\), and thus \(S\) is linearly independent. Also, since \(S\) is an infinite set, so if there is a basis \(b\) of \(V\), then \(b\) must also be an infinite set, which means \(V\) is not finite-dimensional.      
\end{proof}

\begin{problem}
Consider the differentiation transformation on \(V=\mathbb{R}[x]\), which is defined by 
\[
  D(f(x)) = f^{\prime} (x) \quad \forall f(x) \in V.  
\] 
Find the range and null space of this transformation.
\end{problem}
\begin{proof}
    Since for all \(f(x) = a_0 + a_1 x + \dots + a_n x^n\), we know 
    \[
        F(x) = C + a_0 x + \frac{a_1}{2} x^2 + \dots + \frac{a_i}{i+1}x^{i+1} + \dots + \frac{a_n}{n+1}x^{n+1}
    \] has \(F^{\prime} (x) = f(x)\), where \(C\) can be any element in \(\mathbb{R} \). Also, we have \(F(x) \in \mathbb{R} [x]\) and \(D(F(x))=f(x)\), so \(f(x) \in \Im (D)\), which means \(\Im (D) = \mathbb{R} [x]\).
    
    Now if for some \(f(x) \in \mathbb{R} [x]\), we have \(D(f(x)) = 0\), then we know \(f(x)\) is a constant function, so
    \[
        \ker D = \left\{ f(x) \in \mathbb{R} [x] \mid f(x) = c \text{ for some } c \in \mathbb{R}  \right\}.
    \]   
\end{proof}

\begin{problem}
    Let \(V\) be the vector space of all \(n \times n\) matrices over the field \(F\), and let \(B\) be a fixed \(n \times n\) matrix. If 
    \[
        T(A) = AB-BA,
    \]verify that \(T\) is a linear transformation from \(V\) into \(V\).   
\end{problem}
\begin{proof}
It is trivial that \(T\) is a map from \(V\) into \(V\). Now we show that \(T\) is a linear map. Note that for all \(A, C \in M_{n \times n}(F)\), we have
\begin{align*}
    T(\alpha A + C) &= (\alpha A + C)B - B(\alpha A + C) \\
    &= \alpha AB + CB - \alpha BA - BC \\
    &= \alpha (AB - BA) + (CB - BC) \\
    &= \alpha T(A) + T(C).
\end{align*}   
Hence, \(T\) is a linear map.
\end{proof}

\begin{problem}
    Let \(V\) be the set of all complex numbers regarded as a vector space over the field of real numbers (usual operations). Find a function from \(V\) into \(V\) which is a linear transformation on the above vector space, but which is not a linear transformation on \(C^1\), i.e., which is not complex linear.
\end{problem}
\begin{proof}
    We can consider \(T:V \to V\), where
    \[
        T(a+ bi) = (a + b) + bi \quad \forall a+bi \in V \text{ with }a,b \in \mathbb{R}.
    \] 
    We first show that it is a linear transformation on \(V\). For any \(\alpha \in \mathbb{R} \), and \(a^{\prime} + b^{\prime} i \in V\) with \(a^{\prime} ,b^{\prime} \in \mathbb{R}\),
    \begin{align*}
        T(\alpha (a + bi) + (a^{\prime} + b^{\prime} i)) &= T((\alpha a + a^{\prime} ) + (\alpha b + b^{\prime} )i) \\
        &= (\alpha (a + b) + a^{\prime} + b^{\prime} ) + (\alpha b + b^{\prime} )i \\
        &= (\alpha (a+b) + \alpha b i) + (a^{\prime} +b^{\prime}  + b^{\prime} i) \\
        &= \alpha T(a + bi) + T(a^{\prime} +b^{\prime} i).
    \end{align*}
    Hence, \(T\) is linear on \(V\). Now we show that \(T\) is not complex linear. 
    For \(\alpha = p + qi \in \mathbb{C} \), where \(p, q \in \mathbb{R} \), we know 
    for any \(a + bi \in V\) with \(a, b \in \mathbb{R} \), we have 
    \begin{align*}
        T((p+qi)(a+bi)) &= T((pa-qb) + (pb+qa)i) \\
        &= (pa-qb+pb+qa)+(pb+qa)i,
    \end{align*}    
    but we also have 
    \begin{align*}
        (p + qi)T(a + bi) &= (p + qi)((a+b) + bi) \\
        &= (p + qi)(a + b) + (p + qi)bi \\
        &= pa + pb + qai + qbi + pbi - qb \\
        &= (pa + pb - qb) + (qa + qb + pb)i
    \end{align*}
    Note that
    \[
        T((p+qi)(a+bi)) - (p+qi)T(a+bi) = qa-qbi=q(a-bi).
    \]
    If we pick \(a \neq b\) and \(q \neq 0\), then \(T((p+qi)(a+bi)) \neq (p+qi)T(a+bi)\). Thus, \(T\) is not complex linear. 
\end{proof}
\begin{problem}
    Let \(V\) be a vector space and \(T\) a linear transformation from \(V\) into \(V\). Prove that the following two statements about \(T\) are equivalent.
    \begin{itemize}
        \item [(a)]The intersection of the range of \(T\) and the null space of \(T\) is the zero subspace of \(V\).
        \item [(b)]If \(T(T(\alpha )) = 0\), then \(T(\alpha )=0\).  
    \end{itemize}
\end{problem}
\begin{proof}
    \begin{align*}
        &\ker T \cap \Im T = \left\{ 0 \right\} \\
        \iff &\text{If } w \in \ker T \text{ for some } w \in \Im T, \text{ then } w = 0. \\
        \iff &\text{If } T(w) = 0 \text{ for some } w \in \Im T, \text{ then } w = 0. \\
        \iff &\text{If } T(T(\alpha )) = 0 \text{ for some } \alpha \in V, \text{ then } T(\alpha ) = 0.   
    \end{align*}    
\end{proof}