\lecture{11}{7 April.}{}
Now we explain why Hungarian Algorithm is correct.

\begin{remark}
    Observe that \(\varepsilon > 0\), since if \(x \notin R\) and \(y \notin T\), then \(\left\{ x, y \right\} \) is not covered by \(Q\). Hence, \(\left\{ x, y \right\} \notin E(G_{u, v}) \). This shows \(w(\left\{ x, y \right\} ) < u(x) + v(y)\).       
\end{remark}

\begin{proposition}
After the update step, the pair \(c = (u,v)\) remains a weighted cover, i.e.,
\[
u(x) + v(y) \ge w(x,y), \quad \forall (x,y) \in E.
\]
\end{proposition}

\begin{proof}
Let \(u', v'\) denote the updated functions. We verify that
\[
u'(x) + v'(y) \ge w(x,y), \quad \forall (x,y) \in E,
\]
by considering all possible cases.

\medskip

\textbf{Case 1:} \(x \in R,\; y \notin T.\)

In this case, no update is applied:
\[
u'(x) = u(x), \quad v'(y) = v(y).
\]
Hence,
\[
u'(x) + v'(y) = u(x) + v(y) \ge w(x,y),
\]
since \(c = (u,v)\) is a weighted cover.

\medskip

\textbf{Case 2:} \(x \in R,\; y \in T.\)

We have:
\[
u'(x) = u(x), \quad v'(y) = v(y) + \varepsilon.
\]
Thus,
\[
u'(x) + v'(y) = u(x) + v(y) + \varepsilon \ge w(x,y),
\]
again using the feasibility of \(c\).

\medskip

\textbf{Case 3:} \(x \notin R,\; y \in T.\)

Here,
\[
u'(x) = u(x) - \varepsilon, \quad v'(y) = v(y) + \varepsilon,
\]
so
\[
u'(x) + v'(y) = u(x) + v(y) \ge w(x,y).
\]

\medskip

\textbf{Case 4:} \(x \notin R,\; y \notin T.\)

In this case,
\[
u'(x) = u(x) - \varepsilon, \quad v'(y) = v(y),
\]
and hence
\[
u'(x) + v'(y) = u(x) + v(y) - \varepsilon.
\]

By the definition of \(\varepsilon\),
\[
\varepsilon = \min_{\substack{x \notin R \\ y \notin T}} 
\bigl( u(x) + v(y) - w(x,y) \bigr),
\]
it follows that for all \(x \notin R, y \notin T\),
\[
\varepsilon \le u(x) + v(y) - w(x,y).
\]
Rearranging gives
\[
u(x) + v(y) - \varepsilon \ge w(x,y),
\]
and therefore
\[
u'(x) + v'(y) \ge w(x,y).
\]

\medskip

Since all cases satisfy the inequality, we conclude that \(c' = (u',v')\) is still a weighted cover.
\end{proof}

\begin{remark}
When we update the weighted cover from $(u, v)$ to $(u', v')$, the current matching $M$ remains a valid matching in \(G_{u^{\prime}, v^{\prime} }\). To show this, we have to show for every \(\left\{ x, y \right\}  \in M\), \(\left\{ x, y \right\} \in G_{u^{\prime} , v^{\prime}} \), then since all edges in \(M\) are in \(G_{u^{\prime} , v^{\prime} }\), and vertices in \(G_{u^{\prime} , v^{\prime} }\) is same as \(G_{u, v}\), so \(M\) is still a matching in \(G_{u^{\prime} , v^{\prime} }\). Now we show every \(\left\{ x, y \right\} \in M \) is in \(G_{u^{\prime} , v^{\prime} }\). Note that \(M\) is a maximum matching of \(G_{u, v}\). Thus, \(\left\{ x, y \right\} \) satisfies \(w(x, y) = u(x) + v(y)\). Now since \(Q\) is a minimum vertex cover of \(G_{u, v}\), so \(\left\{ x, y \right\} \) is covered by \(Q\), i.e. \(x\) or \(y\) is in \(Q\). Note that exactly one of \(x, y\) is in \(Q\), since \(\vert Q \vert = \vert M \vert  \) (since \(G_{u, v}\) is bipartite) and \(Q\) covers \(M\). Thus, either \(x \in R, y \notin T\) or \(x \notin R, y \in T\) will occur, and each case we have \(u(x) + v(y) = u^{\prime} (x) + v^{\prime} (y)\), so we're done.    

Consequently, the size of a maximum matching in the equality graph does not decrease:
\[
\alpha'(G_{u',v'}) \ge \alpha'(G_{u,v}).
\]

\medskip

Let us consider the set of $M$-unsaturated vertices in $X$, i.e., vertices not covered by $M$. 
After the update, for each $M$-unsaturated vertex $x \in X$, we explore the $M$-alternating paths in $G_{u',v'}$. 
The update rule for $(u',v')$ (Case 4 above, since some edges \(\left\{ x^{\prime} , y^{\prime}  \right\} \) has \(\varepsilon = u(x^{\prime} ) + v(y^{\prime} ) - w(x^{\prime} , y^{\prime} )\)) ensures that at least one new edge in $G_{u',v'}$ connects some vertex $x^{\prime}  \notin R$ to a vertex $y^{\prime}  \notin T$, 
which was previously not in the equality graph. Now since this new edge \(\left\{ x^{\prime} , y^{\prime}  \right\} \) has \(x^{\prime} \notin R\) and \(y^{\prime} \notin T\), and since \(R = Q \cap X\), where \(Q = T^{\prime} \cup (X \setminus S^{\prime} )\), where 
\begin{align*}
    U &= \left\{ \text{vertices in } X \text{ that are unsaturated by } M  \right\} \\ 
    S^{\prime} &= \left\{ \text{vertices in } X \text{ that can be reached through } M\text{-alternating from } U    \right\} \\
    T^{\prime} &= \left\{ \text{vertices in } Y \text{ that can be reached through } M\text{-alternating from } U    \right\},
\end{align*}
so if \(x \notin R = Q \cap X = X \setminus S^{\prime} \), then \(x\) can be reached from \(U\) through \(M\)-altenating path. However, \(y \notin T = Q \cap Y = T^{\prime}\), which means \(y\) cannot be reached from \(U\) through \(M\)-alternating path.       
This means the update creates a new vertex in $Y$ that can be reached by an $M$-alternating path from $x$, so the alternating tree enlarges. 

Now we may think the edges in Case 2 disappear in \(G_{u^{\prime} , v^{\prime}}\) after the update, will it affect? In fact, if \(\left\{ x_1, y_1 \right\} \) is a Case 2 edge appears in \(G_{u, v}\), then \(x_1 \in R\) and \(y_1 \in T\). This shows \(x_1\) cannot be reached from \(U\) through \(M\)-alternating path and \(y_1\) can. However, \(\left\{ x_1, y_1 \right\} \notin M\) since we have shown that for any edge in \(M\), either \(x_1 \in R\) or \(y_1 \in T\). Hence, under this condition, \(\left\{ x_1, y_1 \right\} \) is useless for enlarging alternating tree.                

\medskip

Since there are at most $n$ vertices in $Y$, after at most $n$ iterations of expanding the alternating tree from an $M$-unsaturated vertex in $X$, 
we either reach an $M$-unsaturated vertex in $Y$ or we add a new reachable vertex to the equality graph. 
In the former case, an $M$-augmenting path exists, allowing us to increase the size of the matching by flipping edges of this augmenting paths:
\[
|M| \longrightarrow |M| + 1.
\]

\medskip

Because the maximum size of a matching in a bipartite graph with $n$ vertices on each side is $n$, 
this argument implies that within at most $n^2$ iterations, we must obtain a perfect matching. 
Thus, the algorithm terminates with a perfect matching, and the process is guaranteed to converge.
\end{remark}


\section{Stable Matching Problem}
Suppose we have a bipartite graph \(G = (X \cup Y, E)\), where \(\vert X \vert = \vert Y \vert  \), then we can define preference lists: 
\paragraph{Preference lists} Each vertex ranks the vertices on the other side in order of preference, i.e. \(\forall x \in X\), \(\exists \pi ^{(x)} \in S_Y\) and \(\forall y \in Y\), \(\exists \pi ^{(y)} \in S_X\).

\begin{definition}
    Given a matching \(M\), a pair \(\left\{ x, y \right\} \notin M \) is an unstable pair if \(x\) prefers \(y\) to their \(M\)-partner and \(y\) prefer \(x\) to their \(M\)-partner. A perfect matching \(M\) is a stable matching if there are no unstable pairs.         
\end{definition}

\begin{theorem}[Gale-Shapley, 1962]
    A stable matching always exists.
\end{theorem}

\subsection{Gale-Shapley Proposal Algorithm}
Every night, every man proposes to their top-ranked woman who haven't reject them. If every women receives exactly one proposal, then stop, and there is a stable matching formed by the woman and the man who proposed to her. Otherwise, every woman says "maybe" to her top suitor and rejects any other. 

\begin{remark}
    In each round, if a woman says "maybe" to a man, then this man can propose again to this woman in next round, but the men who are rejected by the woman cannot.
\end{remark}

\begin{remark}
    If the man receive "maybe" from a woman, then he will propose to this woman in the following rounds until he is rejected or the algorithm ends.
\end{remark}

\begin{claim}
    If the algorithm produces a matching, then it is stable. 
\end{claim}
\begin{explanation}
    Suppose not, suppose man \(x\) is matched with woman \(y\) and man \(x^{\prime} \) is matched with woman \(y^{\prime} \), and \(\left\{ x, y^{\prime} \right\} \) is an unstable pair. Note that in the algorithm, the men move down their preference lists, the women move up their preference lists, so \(x\) proposed to \(y^{\prime} \) before proposing to \(y\), and \(y^{\prime} \) only rejected \(x\) because she had a better option, so she prefer \(x^{\prime} \) to \(x\) (If \(y^{\prime} \) prefer \(x\) more than \(x^{\prime}\), then when \(y^{\prime}\) rejects \(x\), there will always be a better option than \(x\) in the following rounds, but then when \(x^{\prime}\) propose to \(y^{\prime}\), \(x^{\prime}\) will not be the best option and thus \(x^{\prime} \) will be rejected by \(y^{\prime}\)), so \(\left\{ x, y^{\prime}  \right\} \) is not a unstable pair, which is a contradiction.             
\end{explanation}

\begin{claim}
    The algorithm terminates.
\end{claim}
\begin{explanation}
    Suppose in an iteration, the \(i\)-th man is proposing to the \(j_i\)-th woman on their list (initially \(j_i = 1\) for all \(i\)). Then, \(\sum_{i=1}^n j_i \) is strictly increasing with every iteration. (If every man propose to different woman, then the algorithm ends. If two men propose to same woman, then one of them will be rejected and thus \(\sum_{i=1}^n j_i \) increases in next round) Thus, it terminates within \(n^2\) iterations. 
\end{explanation}

\begin{claim}
    The algorithm always produces a matching.
\end{claim}