\lecture{5}{13 March.}{}
\section{Running Time of Dijkstra's Algorithm}
Since we have \(n - 1\) iterations, and in each iteration, we have to find the minimum, which takes \(O(n)\) steps, and updating also takes \(O(n)\) steps, so the total running time is \(O\left( n^2 \right) \).

\section{Traveling Salesman Problem}
\begin{problem}[Traveling Salesman Problem]
    If we have a weighted graph \(G=(V,E)\), where each vertex is a city and each edge is a road between two cities, and we are at \(v \in V\) initially. Then, how to travel to every city exactly once and then return to the starting point \(v\) while minimizin the cost?   
\end{problem}

\begin{definition}[Hamilton cycle]
    A cycle that goes through every vertex in a graph is called a Hamilton cycle.
\end{definition}

\begin{remark}
    Traveling Salesman Problem's goal is to find a Hamilton cycle of minimum cost of the given graph.
\end{remark}

\begin{observation}
    The number of possible routes is \(\frac{1}{2} (n - 1)!\) since we can just permutate the \(n - 1\) vertices that is not the starting point, and note that the direction is not important, so \(u \to a \to b \to u\) and \(u \to b \to a \to u\) is considered same routes.     
\end{observation}

Thus, the brute force takes \(O(n) \cdot \frac{1}{2} (n - 1)! = O(n!)\) time since for each route we have to go through this path to compute the cost.

\begin{remark}
    The Held-Karp Algorithm, which uses dynamic programming, takes \(O\left( n^2 2^n \right) \) time to solve Traveling Salesman Problem (also exponential in memory). 
\end{remark}

\begin{question}[Open question]
    \hfil
    \begin{itemize}
        \item Is there a polynomial time algorithm?
        \item Is there an algorithm takes \(O(1.99999999^n)\) time?
    \end{itemize}
\end{question}