\section{Upper Bound and Lower Bound}
\lecture{2}{9 July. 08:00}{}
\begin{definition}
	Let \(S \subseteq \mathbb{R} \) and \(r \in \mathbb{R} \). We say that
	\begin{itemize}
		\item \(r\) is a upper (resp. lower) bound of \(S\) if \(\forall s \in S\), \(r \ge\) (resp. \(\le\) ) \(s\). 
		\item \(r\) is the greatest/largest/highest (resp. least/smallest/lowest) element of \(S\) if \(r\) is a upper (resps lower) bound of \(S\) and \(r \in S\). 
		\begin{notation}
			\(r = \max S\) (resp. \(\min S\) ). 
		\end{notation}
		\item   \(r\) is the least upper (greatest lower) bound of \(S\) if \(r = \min \left\{ u \in \mathbb{R} \mid u \text{ is a upper bound of } S \right\} \) (resp. \(r = \max \left\{ l \in \mathbb{R} \mid l \text{ is a lower bound of } S \right\} \) ).
		\begin{notation}
			\(r = \sup S\) (resp. \(\inf S\).) 
		\end{notation}          
	\end{itemize}  
\end{definition}

\begin{remark}
	Every \(r \in \mathbb{R} \) is a upper bound of \(\varnothing \) .
\end{remark}

\begin{note}
\begin{itemize}
	\item 	We write \(\sup S = \infty \) (resp. \(\inf S = \infty \) ) if and only if \(S\) has no upper (resp. lower) bound. If this is the case, we say \(\sup S\) (resp. \(\inf S\) ) doesn't exist.  
	\item \(S\) is bounded above (resp. below) iff \(S\) has a upper (resp. lower) bound.  
\end{itemize}  
\end{note}

\begin{definition}[Dedekind cut]
	Let \(A, B \subseteq \mathbb{R} \). We say that \((A,B)\) is a Dedekind cut (of \(\mathbb{R} \) ) if 
	\begin{enumerate}
		\item \(A \neq \varnothing \neq B\) 
		\item \(A \cup  B = \mathbb{R} \)
		\item \(\forall a \in A, \ b \in B\) we have \(a < b\).
	\end{enumerate}   
	We usually call \(A\) (resp. \(B\)) the lower (resp. upper) part of \((A,B)\).    
\end{definition}

\begin{theorem}\label{thm: Dedekind's gapless}
	From now on (until Professor Chi say stop), we assume that \(\mathbb{R} \) has the following property (Dedekind's gapless property): If \((A,B)\) is a D-cut of \(\mathbb{R} \), then exactly one of the following happens: 
	\begin{enumerate}
		\item \(\max A\) exists but \(\min B\) doesn't;
		\item \(\min B\) exists but \(\max A\) doesn't.    
	\end{enumerate}  
	We call the \(\max A\) in 1. (resp. \(\min B\) in 2. ) the cutting of \((A,B)\).  
\end{theorem}

\begin{exercise}
	We may define Dedekind cuts of \(\mathbb{Q}, \ \mathbb{Z}  \) similarly. Does the Dedekind gapless property hold for \(\mathbb{Q} \) or \(\mathbb{Z} \) ? 
\end{exercise}
Hint: Consider \(B = \left\{ x \in \mathbb{Q} \mid x > 0, x^2 > 2 \right\} \). We are allowed to use the fact that there does not exist a rational number \(x\) such that \(x^2=2\).   

\begin{theorem}[Weierstrass]\label{thm: Weierstrass}
	Let \(\varnothing \neq S \subseteq \mathbb{R} \). If \(S\) has a upper bound, then \(\sup S\) exists.   
\end{theorem}
\begin{proof}
	Let \(B\) be the set of every upper bound of \(S\) and suppose \(A\coloneqq \mathbb{R} \backslash B\). We need to show that \(\min B\) exists. We first show that \((A,B)\) is a Dedekind cut of \(\mathbb{R} \).
	
	Since we know \(S\) is not empty, so we know \(\forall s \in S\), \(s-1\) is not an upper bound, and thus \(s-1 \in A\), which means \(A\) is not empty, and we know \(B\) is not empty by the description of the problem. 
	
	Also, it is trivial that \(A \cup B = \mathbb{R} \). 
	
	For \(a \in A\) and \(b \in B\), we need to show that \(a < b\). Were this false, \(a \ge b\), and hence \(a\) is a upper bound of \(S\) since \(b\) is a upper bound, so \(a \in B\). However, \(A \cap B = \varnothing \). Hence, we have shown that \((A,B)\) is a Dedekind cut of \(\mathbb{R} \). 
	
	Now we want to use Dedekind's gapless property to say that we must have \(\min B\) exists. Were this false, we know \(\max A\) exists, denoted by \(a_0\). Note that \(a_0 \in A\), so \(a_0 \notin B\), and thus \(a_0\) is not an upper bound of \(S\). Hence, there exists \(s_0 \in S\) such that \(s_0 > a_0\), but this implies \(s_0 \notin A\), so \(s_0 \in B\), and thus \(s_0\) is a upper bound of \(S\). Now choose some \(x\) such that \(a_0 < x < s_0\), so \(x \in B\) and thus \(x\) is an upper bound of \(S\), but we have \(x < s_0 \in S\), which is a contradiction.         
\end{proof}

\begin{theorem}[the Archimedean Property]\label{thm: Archimedean}
	Prove the following statement: \(\forall r \in \mathbb{R} \), then \(r > 0\) implies that \(\exists n \in \mathbb{N} \) such that \(\frac{1}{n} < r\).    
\end{theorem}
Hint: Rephrase this statement in a way linking it to the upper bound of the set \(S = \mathbb{N} \subseteq \mathbb{R}\). 

\section{Sequence}
\begin{definition*}
	We can define the limit of the sequence as follow.
\begin{definition}
		Let \(a_n (n \in \mathbb{N} )\) or \(\left\{ a_n \right\}_{n=1}^{\infty}  \) be a sequence in \(\mathbb{R} \) and \(L \in \mathbb{R} \). We say that \(a_n\) converges to \(L\) (as \(n \to \infty \)) if \(\forall \varepsilon > 0, \ \exists N \in \mathbb{N} \) such that \(n \ge N\) implies \(\left\vert a_n - L \right\vert < \varepsilon  \). 
\end{definition}    

\begin{notation}
	\(\lim_{n \to \infty} a_n = L \). 
\end{notation}

\begin{note}
	If such \(L\) exists, we call it the limit of \(a_n\) and we call \(\left\{ a_n \right\} \) a convergent sequence, otherwise we call it a divergent sequence.   
\end{note}

\begin{definition}
	\(\lim_{n \to \infty} a_n = \infty (-\infty )  \) means \(\forall M \in \mathbb{R} , \ \exists N \in \mathbb{N} \) such that \(n > N\) implies \(a_n \ge (\le) M\).  
\end{definition}
\end{definition*}

\begin{exercise}
\begin{enumerate}	
	\item 	\(\lim_{n \to \infty} a_n = L \) and \(\lim_{n \to \infty} a_n = M\) implies \(L=M\).  
	\item \(\left\{ a_n \right\} \) is convergent implies \(\left\{ a_n \right\} \) is bounded.  
	\item Suppose we have \(\left\{ a_n \right\}, \ \left\{ b_n \right\}  \), and \(a_n \le b_n\) for all \(n \in \mathbb{N} \), and \(\lim_{n \to \infty} a_n = L \), \(\lim_{n \to \infty} b_n = M \), prove that \(L \le M\). What if \(\le\) is replaced by \(<\), is this statement still correct?  
\end{enumerate} 
\end{exercise}

\begin{remark}
	Changing or removing finitely many terms in \(a_n\) does not affect \(\left\{ a_n \right\} \) is convergent or not (and its limit).   
\end{remark}

\begin{proposition}
	If \(\lim_{n \to \infty} a_n = L\) and \(\lim_{n \to \infty} b_n = M \), then
	\begin{enumerate}
		\item \(\lim_{n \to \infty} (a_n \pm b_n) = L \pm M\). 
		\item \(\lim_{n \to \infty} a_n \cdot b_n = LM \). 
		\item If \(M \neq 0\), then \(b_n \neq 0\) for all but finitely many \(n\), and \(\lim_{n \to \infty} \frac{a_n}{b_n} = \frac{L}{M} \).       
	\end{enumerate}  
\end{proposition}
\begin{proof}[proof of 1.]
	Consider \(\left\vert (a_n \pm b_n) - (L \pm M) \right\vert \). We can see that 
	\begin{align*}
		\left\vert (a_n \pm b_n) - (L \pm M) \right\vert &= \left\vert (a_n - L) \pm (b_n - M) \right\vert \le \left\vert a_n - L \right\vert + \left\vert b_n - M \right\vert   .
	\end{align*}
	Also, we know \(\forall \varepsilon > 0, \ \exists N_1, N_2 \in \mathbb{N} \) such that \(n \ge N_1 \implies \vert a_n - L \vert < \varepsilon  \) and \(n \ge N_2 \implies \vert b_n - M \vert < \varepsilon  \). Let \(N = \max \left\{ N_1, N_2 \right\} \), then \(n \ge N\) implies 
	\[
		\left\vert (a_n \pm b_n) - (L \pm M) \right\vert \le \left\vert a_n - L \right\vert + \left\vert b_n - L \right\vert < \varepsilon + \varepsilon  = 2\varepsilon .   
	\]     
	Hence, we can pick \(\varepsilon_1 = \frac{\varepsilon}{2} = \varepsilon _2\) so that \(n \ge N_1^{\prime} \implies \vert a_n - L \vert < \varepsilon _1 = \frac{\varepsilon}{2} \) and \(n \ge N_2^{\prime} \implies \vert b_n - M \vert < \varepsilon _2 = \frac{\varepsilon}{2} \), and thus we know \(n \ge \max \left\{ N_1^{\prime} , N_2^{\prime}  \right\} \) implies that 
		\[
		\left\vert (a_n \pm b_n) - (L \pm M) \right\vert \le \left\vert a_n - L \right\vert + \left\vert b_n - L \right\vert < \frac{\varepsilon}{2} + \frac{\varepsilon}{2}  = \varepsilon .   
	\]      
\end{proof}
\begin{proof}[proof of 2.]
	Consider \(\left\vert a_n b_n - LM \right\vert \). Notice that 
	\[
		\left\vert a_n b_n - LM \right\vert = \left\vert a_n b_n - L b_n + Lb_n - LM \right\vert \le \vert a_n - L \vert \vert b_n \vert + \vert L \vert \vert b_n - M \vert.      
	\] 
	If we can choose \(C>0\) such that \(\vert b_n \vert \le C \) for all \(n \in \mathbb{N} \) and \(\vert L \vert \le C \), then  we have 
	\[
		\vert a_n - L \vert \vert b_n \vert + \vert L \vert \vert b_n - M \vert \le C \vert a_n - L \vert + C \vert b_n - M \vert.      
	\]    Hence, we want to find some \(N_1, N_2\) such that \(\forall \varepsilon > 0\), we have \(n \ge \max \left\{ N_1, N_2 \right\} \) implies \(\vert a_n - L \vert \le \frac{\varepsilon}{2C} \) and \(\vert b_n - M \vert \le \frac{\varepsilon}{2C} \), and then we're done. 
	
	Now since \(\left\{ b_n \right\} \) is convergent, so it is bounded and thus we can pick such \(C\) by a previous exercise. 
\end{proof}
\begin{proof}[proof of 3.]
We only need to prove \(\lim_{n \to \infty} \frac{1}{b_n} = \frac{1}{M}\), and removing the terms being zeros will not affect the convergence of this sequence.
\end{proof}

\begin{note}
	What if \(L,M= \pm \infty\)? 
\end{note}

\begin{exercise}
	Suppose \(a_n = \frac{1 - \left( \frac{1}{2} \right)^n }{1 - \frac{1}{2}}\), then \(\lim_{n \to \infty} a_n = \frac{1}{1 - \frac{1}{2}} \).
\end{exercise}






